Particle-in-cell simulation of ion and electron acceleration in trans-relativistic shocks.

### 2017-11-10 papers/Physica2017/Romansky_Physica2017.tex
fz

\begin{abstract}
The problem of Cosmic Ray (CR) origin and acceleration is a widely discussed problem of
modern astrophysics. It is considered that most likely CR sources are supernova remnant
shock waves. One of the methods to study particle injection and acceleration by shock
waves is a particle-in-cell computer simulation. In this paper we present results of shock
wave simulations based on our self-developed implicit particle-in-cell code. 
\end{abstract}
\input{intro.tex}
\input{model.tex}
\input{test.tex}
\input{shock.tex}
\input{conclusions.tex}
\input{biblio.tex}
\end{document}

>>>>

\begin{abstract}
The problem of Cosmic Ray (CR) origin and acceleration is a widely discussed problem of
modern astrophysics. It is considered that most likely CR sources are 
shock waves in supernova remnants or jets. One of the methods to study particle injection and acceleration by shock
waves is a particle-in-cell computer simulation. In this paper we present results of
simulations of relativistic shock waves with low lorenz-factor, based on our self-developed implicit particle-in-cell code. 
\end{abstract}
\input{intro.tex}
\input{shock.tex}
\input{conclusions.tex}
\input{biblio.tex}
\end{document}

### 2017-11-10 papers/Physica2017/intro.tex
fz

\section{Introduction}
One of the possible sources of high-energy cosmic rays are shock waves in astrophysical collisionless plasma due to the diffusive shock acceleration (DSA) mechanism, see \cite{Bell1978}, \cite{Blandford1978}. Strong magnetic fields are necessary for effective acceleration of charged particles and the observations of the synchrotron emission from supernova remnants (SNRs) show, that the magnetic field there is about 100 times stronger then the interstellar field (see for example \cite{Berezhko2003},\cite{Uchiyama2007}). So strong fields can be produced due to instabilities in anisotropic plasma. One of the most powerful methods to explore processes in collisionless plasma is the Particle-in-Cell simulation. In this work we explore instabilities in the plasma using this method.

>>>>

\section{Introduction}
One of the possible sources of high-energy cosmic rays are shock waves in astrophysical collisionless plasma due to the diffusive shock acceleration (DSA) mechanism, see \cite{Bell1978}, \cite{Blandford1978}. Strong magnetic fields are necessary for effective acceleration of charged particles and the observations of the synchrotron emission from supernova remnants (SNRs) show, that the magnetic field there is about 100 times stronger then the interstellar field (see for example \cite{Berezhko2003},\cite{Uchiyama2007}). So strong fields can be produced due to instabilities in anisotropic plasma. One of the most powerful methods to explore processes in collisionless plasma is the Particle-in-Cell simulation. In this work we explore instabilities in the plasma using this method. 
We developed the implicit particle-in-cell (PIC) code, based on the scheme suggested by Lapenta et al.~\cite{Lapenta2006} and improved for the relativistic case by Noguchi et al.\cite{Noguchi2007}.
Our code is fully three dimensional and parallelized with MPI technology, which is adapted for distributed computing and can be executed on a wide class of computers.
